>

### 2024-12-11 docs/article.qmd
Discuss about polypharmacy findings

>>>>

This study is an egocentric network analysis of two population groups: individuals receiving antidepressants and those receiving anxiolytics. On average, each person received 6 days of polypharmacy regimens in a year. The rate of polypharmacy differs between these two groups. Same-class polypharmacy is more prevalent among individuals treated with antidepressants than among those treated with anxiolytics. Conversely, multi-class polypharmacy is more common in individuals treated with anxiolytics. In both groups, multi-class polypharmacy is ten times more prevalent than same-class polypharmacy. The high prevalence of multi-class polypharmacy in our findings aligns with previous studies, which show that antidepressants and anxiolytics are often co-prescribed with other medications [@Shrivastava2013], and multi-class regimens contribute the most to the prevalence of psychopharmaca polypharmacy [@de2004polypharmacy].

The rate of total polypharmacy in people prescribed with antidepressants

• First paragraph: Discuss about polypharmacy
• Second paragraph: Explain the concordance with other literatures
• Third paragraph: Explain about the DPN
• Fourth paragraph: Strength
• Fifth paragraph: Limitation
  • Lost of individual values
  • Add limitation about weighting the DDD $\to$ How does it reflect augmented polypharmacy?
